Ant Transition Matrix

### 2020-10-23 Ant Matrix_TOM.Rmd
ADded a size distribution figure.

>>>>

```{r ant_size_distributions}
plot(density(log(cactus$volume_t[cactus$ant_t=="vacant"]),na.rm=T),type="l",lwd=3,ylim=c(0,0.3),main=" ",
     xlab="Plant size (log volume)")
lines(density(log(cactus$volume_t[cactus$ant_t=="liom"]),na.rm=T),type="l",lwd=3,col="blue")
lines(density(log(cactus$volume_t[cactus$ant_t=="crem"]),na.rm=T),type="l",lwd=3,col="red")
lines(density(log(cactus$volume_t[cactus$ant_t=="for"]),na.rm=T),type="l",lwd=3,col="green")
lines(density(log(cactus$volume_t[cactus$ant_t=="other"]),na.rm=T),type="l",lwd=3,col="pink")
legend("topleft",legend=c("Vacant","Liom.","Crem.","For.","Other"),pch=16,col=c("black","blue","red","green","pink"),bty="n",lwd=3)

```{r}

par(mfrow=c(2,3))
plot(density(log(cactus$volume_t[cactus$ant_t=="vacant"]),na.rm=T))
points(log(cactus$volume_t[cactus$ant_t=="vacant"]),
       rep(0,times=length(log(cactus$volume_t[cactus$ant_t=="vacant"]))),pch="|")
plot(density(log(cactus$volume_t[cactus$ant_t=="liom"]),na.rm=T))
points(log(cactus$volume_t[cactus$ant_t=="liom"]),
       rep(0,times=length(log(cactus$volume_t[cactus$ant_t=="liom"]))),pch="|")
plot(density(log(cactus$volume_t[cactus$ant_t=="crem"]),na.rm=T))
points(log(cactus$volume_t[cactus$ant_t=="crem"]),
       rep(0,times=length(log(cactus$volume_t[cactus$ant_t=="crem"]))),pch="|")
plot(density(log(cactus$volume_t[cactus$ant_t=="for"]),na.rm=T))
points(log(cactus$volume_t[cactus$ant_t=="for"]),
       rep(0,times=length(log(cactus$volume_t[cactus$ant_t=="for"]))),pch="|")
plot(density(log(cactus$volume_t[cactus$ant_t=="other"]),na.rm=T))
points(log(cactus$volume_t[cactus$ant_t=="other"]),
       rep(0,times=length(log(cactus$volume_t[cactus$ant_t=="other"]))),pch="|")
```
